% !TXS template
\documentclass[11pt,a4paper,roman,english]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\moderncvstyle{banking}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
\usepackage[scale=0.85,a4paper]{geometry}
\usepackage{babel}
\usepackage{import}
%----------------------------------------------------------------------------------
%            personal data
%----------------------------------------------------------------------------------
\firstname{{\huge Jonathan A.}}
\familyname{{\huge Yepez Montenegro}}
\address{2/24 Underhill Avenue, Indooroopilly}{QLD 4068}{Brisbane, Australia} \mobile{+61 435 958 403}
\email{jonathanyepezm@gmail.com}
\begin{document}
%-----       resume       ---------------------------------------------------------
\makecvtitle
\section{Education}
\cventry{2014--2017}{Bachelor of Engineering}{The University of Queensland}{Brisbane, Australia}{First Class Honours}{Graduated with an Extended Major in Mechatronics} 
\cventry{2007--2013}{International Baccalaureate}{ISM International Academy}{Quito, Ecuador}{34/45}{Compelted the IB Program in addition to the National Baccalaureate.}
\section{Achievements and Awards}
Graduate Engineer member of Engineers Australia (since January 2018).\\Awarded the "Dean's Commendation for Academic Excellence" (2014 and 2017).\\Presenter at the School of ITEE Innovation Expo (2017).\\Winter Research Scholar - School of IT and Electrical Engineering at the University of Queensland (2017).\\ Summer Research Scholar - Centre for Advanced Imaging (2016).\\ Member of the Engineering, Architecture and Information Technology Scholars (2015).\\Awarded a scholarship for undergraduate studies from ecuadorian entities SENESCYT and IECE as part of the program "Universities of Excellence" (2013).
\section{Work Experience}
\cventry{November 2017--December 2018}{Engineer Intern}{Bosch Rexroth Australia}{Brisbane, Australia}{}{This is another test}
\cventry{July 2017--August 2017}{Winter Research Scholar}{School of IT and Electrical Engineering at the University of Queensland}{Brisbane, Australia}{}{Worked on an innovative MR image reconstruction algorithm, the project focused on the implementation of GPU accelerated software via Python and TensorFlow for time-efficient reconstruction of images. Collaborated on the validation and testing of the program.}
\cventry{November 2016--January 2017}{Summer Resarch Scholar}{Centre for Advanced Imaging at The University of Queensland}{Brisbane, Australia}{}{As a resedarch scholar, I was involved in projects focused on the analysis and processing of MRI data. Working under the supervision of highly skilled researchers, my role consisted on xxxxx}
\section{Skills}
\subsection{Technical}
\cvitem{}{Programming knowledge in: Matlab/Simulink, Arduino, C, Python and Java.}
\cvitem{}{Use of common laboratory equipment for electrical circuit analysis, design and testing.}
\cvitem{}{Experience with electronic sensors as well as actuators selection and implementation for small scale projects.}
\cvitem{}{Some experience with CAD and 3D printing for prototyping.}
\cvitem{}{Basic knowledge of PLC and HMI Controllers for industrial machinery using BODAS-design3.0 and CODESYS.}
\cvitem{}{Proficient with the use of Microsoft Office, being able to provide professional reports and presentations. Additionally, some experience using LaTex for report generation.}
\cvitem{}{General project planning and estimation together with SAP for production and sales orders.}
\subsection{Social}
\cvitem{}{Good time management and effective when working under pressure.}
\cvitem{}{Easily adapt to different working conditions, collaborating with people from different cultures and backgrounds.}
\cvitem{}{I am passionate about learning new things related to my field of studies, acquiring experiences and sharing ideas with other people. I am a fast learner who finds different perspectives to analyze a problem.}
\cvitem{}{I am highly interested in learning about processes and technologies related to control, robotics and biomedical applications.}
\cvitem{}{I am a positive person with motivation towards achieving common goals in a team. Perseverant and supportive.}
\section{Languages}
\cvitemwithcomment{Spanish}{\quad Native Speaker}{}
\cvitemwithcomment{English}{\quad  Proficient}{}
\cvitemwithcomment{German}{\quad Level B1}{}
\section{Certifications and Courses}
\cventry{October 2018}{Basic Knowledge of Electric Control Technology}{Bosch Rexroth on LearnWorld Portal}{Online}{}{Overview of PLC, CNC, RC Systems as well as interfaces between human and machines}
\cventry{June 2018}{Basic Knowledge of Hydraulic}{Bosch Rexroth on LearnWorld Portal}{Online}{}{Training describing the basic structure of a hydraulic system, function of hydraulic components and basics of hydraulic diagrams.}
\cventry{April 2018}{Electrical Automation Technology Basics}{Bosch Rexroth on LearnWorld Portal}{Online}{}{E-training providing the fundamental of electrical automation technology, interfaces between control systems and machines and an overview of PLC Programming.}
\cventry{February 2018}{Materials Science: 10 Things Every Engineer Should Know}{University of California, Davis on Coursera}{Online}{}{}
\cventry{February 2018}{Fundamentals of Fluid Power}{University of Minnesota on Coursera}{Online}{}{}
\cventry{October 2017}{Introduction to MRI Diffusion}{The Centre for Advanced Imaging}{Brisbane, Australia}{}{}
\cventry{July 2015}{Certificate I in Engineering}{TAFE Queensland SkillsTech}{Brisbane, Australia}{}{Use of workshop machines for basic operations and use of hand tools.}
\cventry{September 2013}{Baccalaureate in Music}{National Conservatory of Music}{Quito, Ecuador}{}{Specialized in classical guitar, performing musical works with a focus on national and contemporary artists.}
\section{Extracurricular Activities and Interests}
\cvitem{Secretary of the Ecuadorian Society (ECSO) at UQ}{Collaborated in cultural events such as the 'Cultural Fiesta', organizing and participating with other students in social events.}
\cvitem{Student Leader at UQ}{Participated in welcoming events for new students, providing information and assistance with regards to studies. Also, offered campus tours to recently enrolled students and shared tips related to university life. The principal programs related to this role were JSAPP (Jump Start Academic Preparation Program) and IAP (Introductory Academic Program)}
\cvitem{UQ Idea Hub}{Participated with two colleagues in the Idea Hub Incubator program, learning about Start-Ups and the initial steps to organize a business idea.}
\cvitem{EAIT Ambassador}{em description, UQ Open Day, Tertiary Studies Expo}
\cvitem{Volunteering}{YOUNG ICTE Explorers, Science and Engineering Challenge, IAPitem description}
\cvitem{Hobbies}{I enjoy swimming, playing football; attending artistic presentations, playing guitar, reading fiction novels; online gaming as well as watching movies with my friends.}
\section{References}
\begin{cvcolumns}
  \cvcolumn{Mr. Rod Elvin}{General Manager\\ Bosch Rexroth Australia\\+61 435958403 \\rod@example.com}
  \cvcolumn{Mr. Guy Bowning}{General Sales Manager\\ Bosch Rexroth Australia\\ +61 44444444 \\ guy@example.com}
  \cvcolumn{Dr. Surya Singh}{Robotics Design Lab Director\\ The University of Queensland\\ +61 7 3365 8328\\ spns@euq.edu.au}
\end{cvcolumns}
\clearpage
\end{document}